### 2011-04-24 docs/architecture/architecture.tex
more work filling in details

To build a \multifab, we need to provide a \layout, the number of
components to store in the multifab, and the number of ghostcells.  In
MAESTRO, the hierarchry of grids will be described by a single
\mllayout.  A \multifab\ can be declared and built at any time in a
simulation using the \mllayout, thereby allocating space at every
grid location in the simulation.  The sequence to build a \multifab\
appears as
\begin{verbatim}
  type(multifab) :: mfab(nlevs)
  ...
  do n = 1, nlevs
     call multifab_build(mfab(n), mla%la(n), nc, ng)
  enddo
\end{verbatim}
Here, {\tt nc} is the number of components and {\tt ng} is the number
of ghostcells.  The \multifab\ is built one level at a time, using the
\layout\ for that level taken from the \mllayout, {\tt mla}.

A common operation on a \multifab\ is to initialize it to $0$
everywhere.  This can be done (level-by-level) as
\begin{verbatim}
call setval(mfab(n), ZERO, all=.true.)
\end{verbatim}
where {\tt ZERO} is the constant 0.0 from {\tt bl\_constants\_module}.

Subroutines to add, multiply, or divide two \multifab s exist, as do
subroutines to copy from one \multifab\ to another---see {\tt boxlib/multifab.f90}
for the full list of routines that work with \multifab s.

@@

\subsection{Other Quantities}

@@

@@

eos module variables

eos input types

@@

@@

\section{Example: Accessing State Data}

@@

\section{Working with Multifabs}

need to describe the routines for adding two multifabs, subtracting,
etc. and norm, etc.

>>>>

To build a \multifab, we need to provide a \layout, the number of
components to store in the multifab, and the number of ghostcells.  In
MAESTRO, the hierarchry of grids will be described by a single
\mllayout.  A \multifab\ can be declared and built at any time in a
simulation using the \mllayout, thereby allocating space at every
grid location in the simulation.  The sequence to build a \multifab\
appears as
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  type(multifab) :: mfab(nlevs)
  ...
  do n = 1, nlevs
     call multifab_build(mfab(n), mla%la(n), nc, ng)
  enddo
\end{lstlisting}
Here, {\tt nc} is the number of components and {\tt ng} is the number
of ghostcells.  The \multifab\ is built one level at a time, using the
\layout\ for that level taken from the \mllayout, {\tt mla}.

A common operation on a \multifab\ is to initialize it to $0$
everywhere.  This can be done (level-by-level) as
\begin{lstlisting}[language={[95]fortran},mathescape=false]
call setval(mfab(n), ZERO, all=.true.)
\end{lstlisting}
where {\tt ZERO} is the constant 0.0 from {\tt bl\_constants\_module}.

The procedure for accessing the data in each grid managed by the \multifab\
is shown in \S~\ref{sec:example}.  
Subroutines to add, multiply, or divide two \multifab s exist, as do
subroutines to copy from one \multifab\ to another---see {\tt boxlib/multifab.f90}
for the full list of routines that work with \multifab s.

@@

@@

The {\tt average} module provides a routine {\tt average} that takes
a multilevel \multifab\ array and averages the full Cartesian data
onto the 1-d base state.

@@

The {\tt eos\_module} declares for convenience the variables that need
appear in the {\tt eos} call argument list.  MAESTRO routines use
these module variables in the EOS call to avoid having to declare 
each quantity in each routine that calls the EOS.

The first argument to the {\tt eos} call is an integer key that
specifies which thermodynamic variables (in addition to the mass
fractions) are used as input.  Options include:

   \begin{center}
   \begin{tabular}{lc}
   \hline
   key            & input quantities \\
   \hline
   eos\_input\_rt       & $\rho$, $T$ \\
   eos\_input\_rh       & $\rho$, $h$ \\
   eos\_input\_tp       & $T$, $p$ \\
   eos\_input\_rp       & $\rho$, $p$ \\
   eos\_input\_re       & $\rho$, $e$ \\
   eos\_input\_ps       & $p$, $s$ \\
   \hline
   \end{tabular}
   \end{center}

@@

The {\tt fill\_3d\_module} provides routines that map from the 1-d
base state to the full Cartesian 2- or 3-d state.  Variations in the
routines allow for cell-centered or edge-centered data on either the
base state or full Cartesian state.

@@

\section{\label{sec:example} Example: Accessing State Data}

@@
